```{r}
library(dplyr)
library(ggplot2)
library(tidyverse)
library(stringr)
library(stringdist)
library(plotly)
library(scales)
library(lubridate)
```

```{r}
new_bb <- read.csv("/Users/jackholland/Downloads/Togetherhood CSVs/AVL_BB_Edited.csv")
View(new_bb)
```



##Getting Ready for MoM, YoY comparisons
```{r}
new_bb <- new_bb %>%
  mutate(Date = as.Date(Date, format = "%m/%d/%Y")) %>%
  mutate(partner_type = ifelse(partner_type == "Big Fish", "Public School", partner_type))

View(new_bb)
```

```{r}
bb_years <- new_bb %>%
  mutate(year = year(Date)) |>
  mutate(year = as.factor(year)) |>
  filter(!Partner == "")

bb_2022 <- bb_years |>
  filter(year == 2022)

bb_2023 <- bb_years |>
  filter(year == 2023)

bb_2024 <- bb_years |>
  filter(year == 2024)
```

##Revenue by Partner Type YoY
```{r}
partner_type_revenue_2022 <- bb_2022 |>
  group_by(partner_type) |>
  summarise(
    Total_Revenue = sum(Revenue, na.rm = TRUE),
    Total_Sessions = n()
    ) |>
  mutate(
    Revenue_Per_Session = Total_Revenue / Total_Sessions,
  )

#View(partner_type_revenue)

######

high_grossing_types <- partner_type_revenue_2022 |>
  arrange(desc(Total_Revenue)) |>
  head(20)

ggplot(high_grossing_types, aes(x = reorder(partner_type, -Total_Revenue), y = Total_Revenue, fill = Revenue_Per_Session)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = comma(Total_Revenue)), vjust = -0.3, size = 3) +  # Add labels above bars
  scale_fill_gradient(low = "seagreen1", high = "seagreen4", name = "Revenue per Session (USD)") +
  scale_y_continuous(labels = comma) +  # Ensure y-axis labels are formatted with commas
  theme_minimal() +
  labs(title = "Revenue by Partner Type (Sep-Dec 2022)",
       x = "Type",
       y = "Revenue") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
partner_type_revenue_2023 <- bb_2023 |>
  group_by(partner_type) |>
  summarise(
    Total_Revenue = sum(Revenue, na.rm = TRUE),
    Total_Sessions = n()
    ) |>
  mutate(
    Revenue_Per_Session = Total_Revenue / Total_Sessions,
  )

#View(partner_type_revenue)

######

high_grossing_types <- partner_type_revenue_2023 |>
  arrange(desc(Total_Revenue)) |>
  head(20)

ggplot(high_grossing_types, aes(x = reorder(partner_type, -Total_Revenue), y = Total_Revenue, fill = Revenue_Per_Session)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = comma(Total_Revenue)), vjust = -0.3, size = 3) +  # Add labels above bars
  scale_fill_gradient(low = "steelblue1", high = "steelblue4", name = "Revenue per Session (USD)") +
  scale_y_continuous(labels = comma) +  # Ensure y-axis labels are formatted with commas
  theme_minimal() +
  labs(title = "Revenue by Partner Type (2023)",
       x = "Type",
       y = "Revenue") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
partner_type_revenue_2024 <- bb_2024 |>
  group_by(partner_type) |>
  summarise(
    Total_Revenue = sum(Revenue, na.rm = TRUE),
    Total_Sessions = n()
    ) |>
  mutate(
    Revenue_Per_Session = Total_Revenue / Total_Sessions,
  )

#View(partner_type_revenue)

######

high_grossing_types <- partner_type_revenue_2024 |>
  arrange(desc(Total_Revenue)) |>
  head(20)

ggplot(high_grossing_types, aes(x = reorder(partner_type, -Total_Revenue), y = Total_Revenue, fill = Revenue_Per_Session)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = comma(Total_Revenue)), vjust = -0.3, size = 3) +  # Add labels above bars
  scale_fill_gradient(low = "slateblue1", high = "slateblue4", name = "Revenue per Session (USD)") +
  scale_y_continuous(labels = comma) +  # Ensure y-axis labels are formatted with commas
  theme_minimal() +
  labs(title = "Revenue by Partner Type (Jan-Jun 2024)",
       x = "Type",
       y = "Revenue") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
bb_years <- bb_years %>%
  mutate(year = as.factor(year))

partner_type_revenue_combined <- bb_years |>
  group_by(partner_type, year) |>
  summarise(
    Total_Revenue = sum(Revenue, na.rm = TRUE),
    Total_Sessions = n()
  ) |>
  mutate(
    Revenue_Per_Session = Total_Revenue / Total_Sessions
  ) |>
  ungroup()

total_revenue_per_partner <- partner_type_revenue_combined |>
  group_by(partner_type) |>
  summarise(Total_Revenue_All_Years = sum(Total_Revenue))

yearly_totals <- partner_type_revenue_combined %>%
  group_by(year) %>%
  summarise(Yearly_Total_Revenue = sum(Total_Revenue))

partner_type_revenue_combined <- partner_type_revenue_combined %>%
  left_join(yearly_totals, by = "year") %>%
  mutate(Percentage = Total_Revenue / Yearly_Total_Revenue * 100)

total_revenue_per_year <- partner_type_revenue_combined %>%
  group_by(year) %>%
  summarise(Total_Revenue_All_Years = sum(Total_Revenue))


ggplot(partner_type_revenue_combined, aes(fill = reorder(partner_type, -Total_Revenue), y = Total_Revenue, x = year)) + 
  geom_bar(position = "stack", stat = "identity") +
  labs(title = "Revenue by Partner Type and Year",
       subtitle = expression(italic("Note: 2022 and 2024 Data Incomplete")),
       x = "Year",
       y = "Total Revenue",
       fill = "Partner Type") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)), position = position_stack(vjust = 0.5), size = 3.5, color = "white") +
  theme_minimal()
```



##Revenue by Course Name and Partner Type (nested)

```{r}
# Summarize the revenue by Course.name and partner_type
course_revenue_summary <- high_grossing_courses %>%
  group_by(Course.name, partner_type) %>%
  summarise(Total_Revenue = sum(Total_Revenue), .groups = 'drop') %>%
  group_by(Course.name) %>%
  summarise(Total_Revenue = sum(Total_Revenue), .groups = 'drop')

# Get the ordered course names by total revenue
ordered_courses <- course_revenue_summary %>%
  arrange(desc(Total_Revenue)) %>%
  pull(Course.name)

# Plot with reordered x-axis
ggplot(high_grossing_courses, aes(x = reorder(Course.name, -Total_Revenue, sum), y = Total_Revenue, fill = partner_type)) + 
  geom_bar(position = "stack", stat = "identity") +
  labs(title = "Top 20 Highest Grossing Courses - Partner Type Composition",
       subtitle = expression(italic("September 2022 - June 2024")),
       x = "Course Name",
       y = "Total Revenue",
       fill = "Partner Type") +
  scale_y_continuous(labels = comma) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
##Revenue based on Primary Category
```{r}
categories_revenue <- bb_years |>
  group_by(category_primary, partner_type) |>
  summarise(
    Total_Revenue = sum(Revenue, na.rm = TRUE),
    Total_Sessions = n()
  ) |>
  mutate(
    Revenue_Per_Session = Total_Revenue / Total_Sessions
  )

high_grossing_categories <- categories_revenue |>
  arrange(desc(Total_Revenue)) |>
  head(20)
```

````{r}
# Summarize the revenue by Category and partner_type
category_revenue_summary <- high_grossing_categories %>%
  group_by(category_primary, partner_type) %>%
  summarise(Total_Revenue = sum(Total_Revenue), .groups = 'drop') %>%
  group_by(category_primary) %>%
  summarise(Total_Revenue = sum(Total_Revenue), .groups = 'drop')

# Get the ordered course names by total revenue
ordered_categories <- category_revenue_summary %>%
  arrange(desc(Total_Revenue)) %>%
  pull(category_primary)

# Plot with reordered x-axis
ggplot(high_grossing_categories, aes(x = reorder(category_primary, -Total_Revenue, sum), y = Total_Revenue, fill = partner_type)) + 
  geom_bar(position = "stack", stat = "identity") +
  labs(title = "Top 20 Highest Grossing Categories - Partner Type Composition",
       subtitle = expression(italic("September 2022 - June 2024")),
       x = "Primary Category",
       y = "Total Revenue",
       fill = "Partner Type") +
  scale_y_continuous(labels = comma) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
##Categories most sold YoY, ToT
```{r}
categories_revenue_2022 <- bb_2022 |>
  group_by(category_primary) |>
  summarise(
    Total_Revenue = sum(Revenue, na.rm = TRUE),
    Total_Sessions = n()
  ) |>
  mutate(
    Revenue_Per_Session = Total_Revenue / Total_Sessions
  )

high_grossing_categories_2022 <- categories_revenue_2022 |>
  arrange(desc(Total_Revenue)) |>
  head(20)

ggplot(high_grossing_categories_2022, aes(x = reorder(category_primary, -Total_Revenue, sum), y = Total_Revenue, fill = Total_Revenue)) + 
  geom_bar(stat = "identity") +
  labs(title = "Top 20 Highest Grossing Categories",
       subtitle = expression(italic("2022")),
       x = "Primary Category",
       y = "Total Revenue",
       fill = "Total Revenue") +
  scale_y_continuous(labels = comma) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
#dig into cullinary category

```{r}
categories_revenue_2023 <- bb_2023 |>
  group_by(category_primary) |>
  summarise(
    Total_Revenue = sum(Revenue, na.rm = TRUE),
    Total_Sessions = n()
  ) |>
  mutate(
    Revenue_Per_Session = Total_Revenue / Total_Sessions
  )

high_grossing_categories_2023 <- categories_revenue_2023 |>
  arrange(desc(Total_Revenue)) |>
  head(20)

ggplot(high_grossing_categories_2023, aes(x = reorder(category_primary, -Total_Revenue, sum), y = Total_Revenue, fill = Total_Revenue)) + 
  geom_bar(stat = "identity") +
  labs(title = "Top 20 Highest Grossing Categories",
       subtitle = expression(italic("2023")),
       x = "Primary Category",
       y = "Total Revenue",
       fill = "Total Revenue") +
  scale_y_continuous(labels = comma) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
categories_revenue_2024 <- bb_2024 |>
  group_by(category_primary) |>
  summarise(
    Total_Revenue = sum(Revenue, na.rm = TRUE),
    Total_Sessions = n()
  ) |>
  mutate(
    Revenue_Per_Session = Total_Revenue / Total_Sessions
  )

high_grossing_categories_2024 <- categories_revenue_2024 |>
  arrange(desc(Total_Revenue)) |>
  head(20)

ggplot(high_grossing_categories_2024, aes(x = reorder(category_primary, -Total_Revenue, sum), y = Total_Revenue, fill = Total_Revenue)) + 
  geom_bar(stat = "identity") +
  labs(title = "Top 20 Highest Grossing Categories",
       subtitle = expression(italic("2023")),
       x = "Primary Category",
       y = "Total Revenue",
       fill = "Total Revenue") +
  scale_y_continuous(labels = comma) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
##Change in Composition, 2023-24
```{r}
bb_years <- bb_years %>%
  mutate(year = as.factor(year))

category_type_revenue_combined <- bb_years |>
  group_by(category_primary, year) |>
  summarise(
    Total_Revenue = sum(Revenue, na.rm = TRUE),
    Total_Sessions = n()
  ) |>
  mutate(
    Revenue_Per_Session = Total_Revenue / Total_Sessions
  ) |>
  ungroup()

total_revenue_per_category <- category_type_revenue_combined |>
  group_by(category_primary) |>
  summarise(Total_Revenue_All_Years = sum(Total_Revenue))

top_5_categories <- total_revenue_per_category |>
  arrange(desc(Total_Revenue_All_Years)) |>
  slice_head(n = 5) |>
  pull(category_primary)

category_type_revenue_combined_top_5 <- category_type_revenue_combined |>
  filter(category_primary %in% top_5_categories)

yearly_totals_category <- category_type_revenue_combined_top_5 %>%
  group_by(year) %>%
  summarise(Yearly_Total_Revenue = sum(Total_Revenue), .groups = 'drop')

category_type_revenue_combined_top_5 <- category_type_revenue_combined_top_5 %>%
  left_join(yearly_totals_category, by = "year") %>%
  mutate(Percentage = Total_Revenue / Yearly_Total_Revenue * 100)

ggplot(category_type_revenue_combined_top_5, aes(fill = reorder(category_primary, -Total_Revenue), y = Total_Revenue, x = year)) + 
  geom_bar(position = "stack", stat = "identity") +
  labs(title = "Revenue by Top 5 Categories and Year",
       subtitle = expression(italic("Note: 2022 and 2024 Data Incomplete")),
       x = "Year",
       y = "Total Revenue",
       fill = "Category") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)), position = position_stack(vjust = 0.5), size = 3.5, color = "white") +
  theme_minimal()
```

```{r}
write.csv(category_type_revenue_combined_top_5, "category_type_revenue_combined_top_5.csv", row.names = FALSE)
```




##Revenue disparities between flat priced courses and price per student fee courses
##by year
#extract classes above 2hr
##explore nesting by partner
##also by category
##pull out july/aug
##course type
##look for one day workshops and maybe pull revenue

```{r}
pricing_pivot <- bb_years %>%
  group_by(Year, Pricing.Plan) %>%
  summarise(
    Total_Revenue = sum(Revenue, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  group_by(Year) %>%
  mutate(
    Total_Revenue_Year = sum(Total_Revenue),  # Total revenue for each year
    Percentage_Total_Revenue = (Total_Revenue / Total_Revenue_Year) * 100  # Percentage for each pricing plan within the year
  ) %>%
  ungroup()

clean_pricing_pivot <- drop_na(pricing_pivot)

ggplot(clean_pricing_pivot, aes(x = factor(Year), y = Total_Revenue, fill = Pricing.Plan)) +
  geom_bar(position = "stack", stat = "identity") +
  geom_text(aes(label = paste0(round(Percentage_Total_Revenue, 1), "%")), 
            position = position_stack(vjust = 0.5), size = 3) +  # Add percentage labels inside bars
  labs(
    title = "Percentage of Total Revenue by Pricing Plan and Year",
    subtitle = expression(italic("September 2022 - June 2024")),
    x = "Year",
    y = "Total Revenue",
    fill = "Pricing Plan"
  ) +
  scale_y_continuous(labels = comma) +
  theme_minimal()

```


